Re-finding to support a Deep Web Question Answering System

### 2010-03-05 trunk/paper/semsearch10/content/results_futurework_conclusion.tex
added better conclusion stuff

In this paper we provide a discussion on a new type of question
answering system that uses previously answered user questions.  We
described our method of modeling a users question answering process
and how we are able to discover semantically similar queries.

\section{Acknowledgements}
Our thanks to Jeff N. Depree, Guillermo Cordero, and Nick Antonelli for thier assistance building this system. Additionally, we would like to thank NSF for their generous support of our project.

>>>>

In this paper we provide a discussion on a new type of question
answering system that uses previously answered user questions.  We
described our method of modeling a users question answering process
and how we are able to discover semantically similar queries.  The Morpheus system still has a lot of room for optimization.  However, we believe this new technique for question answering system will improve the exploration experience.

\section{Acknowledgements}
Our thanks to Guillermo Cordero, and Nick Antonelli for thier assistance building this system. Additionally, we would like to thank NSF for their generous support of our project.
